%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Senior ML Ops Engineer} % Job title % Organization
  {GSK R\&D}
  {New York, United States} % Location
  {Sep 2021 - Current} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item { Developed a Python package and CLI to orchestrate and monitor jobs across AKS and on-prem HPC clusters. Worked directly with research teams on UAT and adoption. }
      \item { Standardized Kubernetes deployments in CI/CD pipeline templates using Helm. Developed Helm charts for realtime- and batch-deployments of machine learning models, and remote development environments. }
      \item { Developed and deployed RESTful API's with FastAPI and Uvicorn to provide a uniform API for Slurm jobs and Argo Workflows. Containerized application with Docker using BuildKit and multistaging. Deployed to an on-prem Kubernetes cluster with Helm and CI/CD pipeline. }
      \item { Created python libraries to reduce code duplication and improve reuse across platform products. Centralized custom types and datamodels with Pydantic. Developed utility packages to standardize logging, parsing of logs, and interactions with Docker images. }
      \item { Spearheaded documentation standards by defining minimum requirements for products lines and products. Used a mixture of Sphinx, Github Pages and Confluence for delivery. }
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer \& Strategy Consultant} % Job title % Organization
    {IBM Services}
    {New York, United States} % Location
    {Feb 2019 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead the implementation of a web application to generate cost and time-estimates for drilling and completing new oil/gas wells. Developed serverless backend services in Python, data ingestion pipeline with spark, and CI/CD pipeline using Ansible and Azure Pipelines.}
        \item {Designed and implemented a machine learning pipeline using a many-models-pattern to perform parallel training and prediction for estimating the ultimate recovery and decline curves for thousands of oil and gas wells.}
        \item {Lead implementation of machine learning models for entity matching problems with a client in the credit industry. Operationalized models in Cloudera Data Science Workbench. Built active learning pipeline to continually collect training data and auditing of labelling. }
        \item {Worked with IBM's external clients to explore data-sources, designed and implemented data pipelines, developed machine learning solutions, deployed solutions in the cloud.}
        \item {Mentored and coached junior developers and data scientists.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist - Machine Learning Engineer} % Job title
    {IBM Analytics} % Organization
    {New York, United States} % Location
    {Jan 2018 - Feb 2019} %
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with external clients on formulating data science projects solving business problems in various industries, through data-discovery and brainstorming sessions.}
        \item {Through a period of up to 90 days, I helped deliver a minimal viable product, encompassing a full pipeline from data ingestion and wrangling to a deployed model.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Data Scientist} % Job title
%     {AOL Inc.} % Organization
%     {New York, United States} % Location
%     {Jun 2017 - Dec 2017} %
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%       \item {Helped build a slack-integrated natural language based bot for obtaining insights and metrics from digital advertisement data.}
%       \item {Responsible for backend software development in Python focusing on data analytics, visualization and presentation using AWS, Spark and D3.js.}
%       \end{cvitems}
%     }
%
% %---------------------------------------------------------
%
% \cventry
%   {Instructor} % Job title
%   {Center of Mathematical Talent, Courant Institute, NYU} % Organization
%   {New York, United States} % Location
%   {Aug 2016 - May 2017} %
%   {
%     \begin{cvitems} % Description(s) of tasks/responsibilities
%     \item {Outreach program for middle and high schools students. Through lectures and problem sessions students were introduced to topics such combinatorics and graph theory.}
%     \end{cvitems}
%   }
%
% %---------------------------------------------------------
%
% \cventry
%   {Teaching Assistant} % Job title
%   {Department of Computer Science, University of Copenhagen} % Organization
%   {Copenhagen, Denmark} % Location
%   {Feb 2015 - Jun 2015} %
%   {
%     \begin{cvitems} % Description(s) of tasks/responsibilities
%     \item {Recitation leader and grader in two classes.}
%     \item {Statistical Models in Science - Introduction to probability theory and statistical methods. Basic statistical modeling, hypothesis testing, model validation and use of R.}
%     \item {Mathematics For Sciences - Introducing tools from mathematical analysis. Power and Fourier series, Fourier transformation, differential equations and vector analysis.}
%     \end{cvitems}
%   }
%
% %---------------------------------------------------------
%
% \cventry
%   {Research Assistant} % Job title
%   {The Image Group, University of Copenhagen} % Organization
%   {Copenhagen, Denmark} % Location
%   {Jul 2014 - Jul 2015} %
%   {
%     \begin{cvitems} % Description(s) of tasks/responsibilities
%     \item {Research Assistant, The Image Group, University of Copenhagen, Copenhagen Researching the connectivity of the human brain.}
%     \item {Preprocessed MRI data for a shortest-path tractography to locate neural fibers. Implemented pre- and post-processing of MRI data sets in Python and modified the shortest-path tractography in C++ for statistical output.}
%     \item {Performed statistical analysis of ~50 million potential nerve fibers per MRI data set through probability distributions.}
%     \end{cvitems}
%   }
%
% %---------------------------------------------------------
%
% \cventry
%   {Mentor} % Job title
%   {Department of Computer Science, University of Copenhagen} % Organization
%   {Copenhagen, Denmark} % Location
%   {Jun 2013 - Jun 2015} %
%   {
%     \begin{cvitems} % Description(s) of tasks/responsibilities
%     \item {Mentored 1st year undergraduate students. Organized an introductory weeks, academic workshops, provided academic guidance, and planned social and events throughout the year.}
%     \end{cvitems}
%   }
%
% %---------------------------------------------------------

\end{cventries}
